### 2017-10-11 Gruba/04-uc.tex

Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \refe{} between $Y'$ and $Z'$ is given by :
%
\begin{equation}
\label{eq:od}
D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2
\end{equation}

As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \refe{} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e
\end{equation}
where $H_e$ refers to the \hd{} over each dimension, with $H_e\ =\ 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e\ =\ 0$ otherwise.

Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity \refe{} is leveraged to compute the distance.
Then, the distance between such two vectors $Y^{\ast}\ = (Y^{\ast}_0, Y^{\ast}_1, ...)$ and $Z^{\ast}\ = (Z^{\ast}_0, Z^{\ast}_1, ...)$ is:
%
\begin{equation}
\label{eq:vd}
D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e
\end{equation}
where $\cdot$ refers to the dot product operation between two normalized vectors $Y^{\ast}_e$ and $Z^{\ast}_e$.

>>>>

Given two numerical vectors $Y'\ = (y'_0, y'_1, ...)$ and $Z'\ = (z'_0, z'_1, ...)$, the \od{} \cite{IEEEexample:books/mk/HanKP2011} between $Y'$ and $Z'$ is given by :
%
\begin{equation}
\label{eq:od}
D_n(Y', Z') = \sum_{\substack{e}} (y_e - z_e)^2
\end{equation}

As to the categorical vectors $Y''\ = (y''_0, y''_1, ...)$ and  $Z''\ = (z''_0, z''_1, ...)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e
\end{equation}
where $H_e$ refers to the \hd{} over each dimension, with $H_e\ =\ 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e\ =\ 0$ otherwise.

Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity is leveraged to compute the distance.
Then, the distance between such two vectors $Y^{\ast}\ = (Y^{\ast}_0, Y^{\ast}_1, ...)$ and $Z^{\ast}\ = (Z^{\ast}_0, Z^{\ast}_1, ...)$ is:
%
\begin{equation}
\label{eq:vd}
D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e
\end{equation}
where $\cdot$ refers to the dot product operation between two normalized vectors $Y^{\ast}_e$ and $Z^{\ast}_e$.

### 2017-10-11 Gruba/05-gm.tex

	\stab(3) \stitle{Interaction Info} includes three correlation metrics. They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
%\end{itemize}
As a result, the obtained group model could learn what does a positive/negative item look like over each metric mentioned above.

>>>>

	\stab(3) \stitle{Interaction Info} includes three correlation metrics. They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
%\end{itemize}
In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem. The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently. As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par
